Homicide Increases in the COVID-19 Era

### 2025-03-07 Draft3.qmd
Added background map to Plot 1

evictions_la <- read.csv("0_Data/Raw_Data/LA_evictions.csv")
```

@@

```{r, echo=FALSE}

@@

>>>>

evictions_la <- read.csv("0_Data/Raw_Data/LA_evictions.csv")

crime_la$year <- as.integer(stringr::str_sub(crime_la$YearWeek, 1, 4))
```

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE}
la_shape <- read_sf(dsn = "0_Data/Raw_Data/ca_counties", layer = "ca_counties")

la_shape <- st_transform(la_shape, crs = 4326)

@@

plot(la_shape$geometry,xlim = c(-119, -118), ylim = c(33.5, 34.5),
     xlab = "Longitude",
  ylab = "Latitude",
  main = "Crime Density (2010-2019)",
  cex.main=0.8)

smoothScatter(
  x    = crime_la_2010_2019$LON,
  y    = crime_la_2010_2019$LAT,
  xlim = c(-119, -118),
  ylim = c(33.5, 34.5),
  nbin = 300,
  xlab = "Longitude",
  ylab = "Latitude",
  main = "Crime Density (2010–2019)",
  colramp = colorRampPalette(c("white", "skyblue", "blue", "darkblue")),
  cex.main=0.8,
  add = TRUE
)

plot(la_shape$geometry,xlim = c(-119, -118), ylim = c(33.5, 34.5),
     xlab = "Longitude",
  ylab = "Latitude",
  main = "Crime Density (2020–Present)",
  cex.main=0.8)

smoothScatter(
  x    = crime_la_2020_present$LON,
  y    = crime_la_2020_present$LAT,
  xlim = c(-119, -118),
  ylim = c(33.5, 34.5),
  nbin = 300,
  xlab = "Longitude",
  ylab = "Latitude",
  main = "Crime Density (2020–Present)",
  colramp = colorRampPalette(c("white", "pink", "red", "darkred")),
  cex.main=0.8, 
  add = TRUE
)
